MINOS Handover Plots

### 2024-10-17 minos/validation/handovers.Rmd

@@

>>>>

tit <- 'Low Income & Material Deprivation Child'

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, low_income_matdep_child)
base.s <- base.dat %>%
  select(pidp, age, time, low_income_matdep_child)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'low_income_matdep_child',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

### Child Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, matdep_child)
base.s <- base.dat %>%
  select(pidp, age, time, matdep_child)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'matdep_child',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```
